Deciding to Disclose: Pregnancy and Alcohol Misuse

### 2014-08-30 Conclusion.tex
Appendix

@@

The conclusions that can be drawn about the behaviours of real life women, and their midwives, are necessarily limited by the paucity of data available to validate the model. While qualitative trends offer a some indication, they are clearly very limited in scope, and do not permit strong claims about the drivers of disclosure, and auger for a sceptical eye as to any recommendations targetted at improving outcomes.  With this said, the trends reported by \citet{Alvik2006}, and \citet{Phillips2007} are bourne out by the model, and predictions from the two more complex rules suggest that encouraging information sharing between women may encourage disclosure, but at the expense of reducing accuracy.

Further work will focus on applying the model to domains where validation data is more available, which will support a more comprehensive evaluation of the model discrepancy.  Disclosure is a widely applicable issue in health and social care and beyond, with examples ranging from a lack of help seeking behaviour noted in older men \citep{Smith2007a}, to the inverse scenario of innapropriate disclosure in social media \citep{christofides2009information}.

>>>>

The conclusions that can be drawn about the behaviours of real life women, and their midwives, are necessarily limited by the paucity of data available to validate the model. While qualitative trends offer a some indication, they are clearly very limited in scope, and do not permit strong claims about the drivers of disclosure, and auger for a sceptical eye as to any recommendations targetted at improving outcomes.  With this said, the trends reported by \citet{Alvik2006}, and \citet{Phillips2007} are bourne out by the model, and predictions from the two more complex rules suggest that encouraging information sharing between women may encourage disclosure, but at the expense of reducing accuracy. As such, further work will focus on applying the model to domains where validation data is more available, which will support a more comprehensive evaluation of the model discrepancy.

@@

 % Disclosure is a widely applicable issue in health and social care and beyond, with examples ranging from a lack of help seeking behaviour noted in older men \citep{Smith2007a}, to the inverse scenario of innapropriate disclosure in social media \citep{christofides2009information}.

### 2014-08-30 SensitivityAnalysis.tex
Appendix

\subsection{Lexicographic}

@@

@@

@@

@@

>>>>

@@

\begin{table}[h!]
\center
\begin{tabular} {|l | l | l | l | l | l |}
\hline
Parameter & Description & Lexicographic & Bayesian Payoff & Bayesian & \ac(CPT) \\ \hline
\(p_{w}(m)\) & Proportion of moderate drinkers & 0.367 & 1.145 \\ \hline
\(p_{w}(l)\) & Proportion of light drinkers & 10.080 & 37.750 \\ \hline
\(p_{m}(m)\) & Proportion of moderate midwives & 6.715 & 13.017\\ \hline
\(p_{m}(l)\) & Proportion of non-judgemental midwives & 43.942 & 1.655 \\ \hline
\(q_{w}\) & Probability of women sharing & 0.198 & 5.527 \\ \hline
\(w_{w}\) & Weight of shared information for women & 0.355 & 13.025 \\ \hline
\(q_{m}\) & Probability of midwives sharing & 0.145 & 0.667 \\ \hline
\(w_{m}\) & Weight of shared information for midwives & 0.118 & 0.376 \\ \hline
\(x_{h}\) & Health payoff for healthy delivery & 0.457 & 9.618 \\ \hline
\(s_{i}[a_{i}]:s_{i}[a_{\neg i}]\) & Psuedo-count favouring honesty & 0.140 & 7.537 \\ \hline
\end{tabular}
\caption[Table caption text]{Median moderate drinker signalling parameter sensitivity. \label{tab:sa_results_sig}}
\end{table}

\begin{table}[h!]
\center
\begin{tabular} {|l | l | l | l | l | l |}
\hline
Rule & \(\sigma^2\) & Nugget \(\sigma^2\) & Mean output & Total output variance & Code uncertainty & RMSSE \\ \hline
Lexicographic & 0.834 & 0.131 &  0.817 & 0.012 & 0.252 & 1.746 \\ \hline
Bayesian Payoff & 1.667 & 0.475 &  0.662 & 0.003 & 0.181 & 3.12 \\ \hline
Bayesian & 0.834 & 0.131 &  0.817 & 0.012 & 0.252 & 1.746 \\ \hline
\ac{CPT} & 0.834 & 0.131 &  0.817 & 0.012 & 0.252 & 1.746 \\ \hline
\end{tabular}
\caption[Table caption text]{Median moderate drinker signalling emulator statistics. \label{tab:sa_emulator_sig}}
\end{table}

@@

\begin{table}[h!]
\center
\begin{tabular} {|l | l | l | l | l | l |}
\hline
Parameter & Description & Lexicographic & Bayesian Payoff & Bayesian & \ac(CPT) \\ \hline
\(p_{w}(m)\) & Proportion of moderate drinkers & 0.367 & 1 \\ \hline
\(p_{w}(l)\) & Proportion of light drinkers & 10.080 & 1 \\ \hline
\(p_{m}(m)\) & Proportion of moderate midwives & 6.715 & 1 \\ \hline
\(p_{m}(l)\) & Proportion of non-judgemental midwives & 43.942 & 1 \\ \hline
\(q_{w}\) & Probability of women sharing & 0.198 & 1 \\ \hline
\(w_{w}\) & Weight of shared information for women & 0.355 & 1 \\ \hline
\(q_{m}\) & Probability of midwives sharing & 0.145 & 1 \\ \hline
\(w_{m}\) & Weight of shared information for midwives & 0.118 & 1 \\ \hline
\(x_{h}\) & Health payoff for healthy delivery & 0.457 & 100 \\ \hline
\(s_{i}[a_{i}]:s_{i}[a_{\neg i}]\) & Psuedo-count favouring honesty & 0.140 & 100:1 \\ \hline
\end{tabular}
\caption[Table caption text]{Median between groups IQR parameter sensitivity. \label{tab:sa_results_iqr}}
\end{table}

\begin{table}[h!]
\center
\begin{tabular} {|l | l | l | l | l | l |}
\hline
Rule & \(\sigma^2\) & Nugget \(\sigma^2\) & Mean output & Total output variance & Code uncertainty & RMSSE \\ \hline
Lexicographic & 0.834 & 0.131 &  0.817 & 0.012 & 0.252 & 1.746 \\ \hline
Bayesian Payoff & 0.834 & 0.131 &  0.817 & 0.012 & 0.252 & 1.746 \\ \hline
Bayesian & 0.834 & 0.131 &  0.817 & 0.012 & 0.252 & 1.746 \\ \hline
\ac{CPT} & 0.834 & 0.131 &  0.817 & 0.012 & 0.252 & 1.746 \\ \hline
\end{tabular}
\caption[Table caption text]{Median between groups IQR emulator statistics. \label{tab:sa_emulator_iqr}}
\end{table}

@@

\begin{table}[h!]
\center
\begin{tabular} {|l | l | l | l | l | l |}
\hline
Parameter & Description & Lexicographic & Bayesian Payoff & Bayesian & \ac(CPT) \\ \hline
\(p_{w}(m)\) & Proportion of moderate drinkers & 0.367 & 1 \\ \hline
\(p_{w}(l)\) & Proportion of light drinkers & 10.080 & 1 \\ \hline
\(p_{m}(m)\) & Proportion of moderate midwives & 6.715 & 1 \\ \hline
\(p_{m}(l)\) & Proportion of non-judgemental midwives & 43.942 & 1 \\ \hline
\(q_{w}\) & Probability of women sharing & 0.198 & 1 \\ \hline
\(w_{w}\) & Weight of shared information for women & 0.355 & 1 \\ \hline
\(q_{m}\) & Probability of midwives sharing & 0.145 & 1 \\ \hline
\(w_{m}\) & Weight of shared information for midwives & 0.118 & 1 \\ \hline
\(x_{h}\) & Health payoff for healthy delivery & 0.457 & 100 \\ \hline
\(s_{i}[a_{i}]:s_{i}[a_{\neg i}]\) & Psuedo-count favouring honesty & 0.140 & 100:1 \\ \hline
\end{tabular}
\caption[Table caption text]{IQR of median moderate drinker signalling parameter sensitivity. \label{tab:sa_results_sig_iqr}}
\end{table}

\begin{table}[h!]
\center
\begin{tabular} {|l | l | l | l | l | l |}
\hline
Rule & \(\sigma^2\) & Nugget \(\sigma^2\) & Mean output & Total output variance & Code uncertainty & RMSSE \\ \hline
Lexicographic & 0.834 & 0.131 &  0.817 & 0.012 & 0.252 & 1.746 \\ \hline
Bayesian Payoff & 0.834 & 0.131 &  0.817 & 0.012 & 0.252 & 1.746 \\ \hline
Bayesian & 0.834 & 0.131 &  0.817 & 0.012 & 0.252 & 1.746 \\ \hline
\ac{CPT} & 0.834 & 0.131 &  0.817 & 0.012 & 0.252 & 1.746 \\ \hline
\end{tabular}
\caption[Table caption text]{IQR of median between groups IQR emulator statistics. \label{tab:sa_emulator_sig_iqr}}
\end{table}

@@

\begin{table}[h!]
\center
\begin{tabular} {|l | l | l | l | l | l |}
\hline
Parameter & Description & Lexicographic & Bayesian Payoff & Bayesian & \ac(CPT) \\ \hline
\(p_{w}(m)\) & Proportion of moderate drinkers & 0.367 & 1 \\ \hline
\(p_{w}(l)\) & Proportion of light drinkers & 10.080 & 1 \\ \hline
\(p_{m}(m)\) & Proportion of moderate midwives & 6.715 & 1 \\ \hline
\(p_{m}(l)\) & Proportion of non-judgemental midwives & 43.942 & 1 \\ \hline
\(q_{w}\) & Probability of women sharing & 0.198 & 1 \\ \hline
\(w_{w}\) & Weight of shared information for women & 0.355 & 1 \\ \hline
\(q_{m}\) & Probability of midwives sharing & 0.145 & 1 \\ \hline
\(w_{m}\) & Weight of shared information for midwives & 0.118 & 1 \\ \hline
\(x_{h}\) & Health payoff for healthy delivery & 0.457 & 100 \\ \hline
\(s_{i}[a_{i}]:s_{i}[a_{\neg i}]\) & Psuedo-count favouring honesty & 0.140 & 100:1 \\ \hline
\end{tabular}
\caption[Table caption text]{IQR of median between groups IQR parameter sensitivity. \label{tab:sa_results_iqr_iqr}}
\end{table}

\begin{table}[h!]
\center
\begin{tabular} {|l | l | l | l | l | l |}
\hline
Rule & \(\sigma^2\) & Nugget \(\sigma^2\) & Mean output & Total output variance & Code uncertainty & RMSSE \\ \hline
Lexicographic & 0.834 & 0.131 &  0.817 & 0.012 & 0.252 & 1.746 \\ \hline
Bayesian Payoff & 0.834 & 0.131 &  0.817 & 0.012 & 0.252 & 1.746 \\ \hline
Bayesian & 0.834 & 0.131 &  0.817 & 0.012 & 0.252 & 1.746 \\ \hline
\ac{CPT} & 0.834 & 0.131 &  0.817 & 0.012 & 0.252 & 1.746 \\ \hline
\end{tabular}
\caption[Table caption text]{IQR of median between groups IQR emulator statistics. \label{tab:sa_emulator_iqr_iqr}}
\end{table}
